---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mlr3summary

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/mlr3summary)](https://CRAN.R-project.org/package=mlr3summary)
[![StackOverflow](https://img.shields.io/badge/stackoverflow-mlr3-orange.svg)](https://stackoverflow.com/questions/tagged/mlr3)
[![Mattermost](https://img.shields.io/badge/chat-mattermost-orange.svg)](https://lmmisld-lmu-stats-slds.srv.mwn.de/mlr_invite/)
<!-- badges: end -->

Concise, informative summaries of machine learning models.
Based on [mlr3](https://github.com/mlr-org/mlr3).
Inspired by the summary output of (generalized) linear models.

## Installation

Install the last release from CRAN:

```{r, eval = FALSE}
install.packages("mlr3summary")
```

Install the development version from GitHub:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("mlr-org/mlr3summary")
```

## Example

### Load data and create a task

```{r, eval = FALSE}
library(mlr3summary)

data("credit", package = "mlr3summary")
task = as_task_classif(credit, target = "risk", positive = "good")
```

### Fit a model and resampling strategy

```{r, eval = FALSE}
set.seed(12005L)
rf = lrn("classif.ranger", predict_type = "prob")
rf$train(task)

cv3 = rsmp("cv", folds = 3L)
rr = resample(task = task, learner = rf, resampling = cv3, store_models = TRUE)
rr$aggregate(msrs(list("classif.acc", "classif.auc")))
```

### Apply the summary function

```{r, eval = FALSE}
summary(object = rf, resample_result = rr)
```

![summary_output](https://github.com/slds-lmu/mlr3summary/assets/25373845/84b6cf8f-72d6-42ae-8218-5df1623008a3)

More examples can be found in [demo/](https://github.com/mlr-org/mlr3summary/tree/master/demo).

## Citation

If you use `mlr3summary`, please cite:

```
Dandl S, Becker M, Bischl B, Casalicchio G, Bothmann L (2024).
mlr3summary: Model and learner summaries for 'mlr3'.
R package version 0.1.0.
```

A BibTeX entry for LaTeX users is

```
  @Manual{,
    title = {mlr3summary: Model and learner summaries for 'mlr3'},
    author = {Susanne Dandl and Marc Becker and Bernd Bischl and Giuseppe Casalicchio and Ludwig Bothmann},
    year = {2024},
    note = {R package version 0.1.0},
  }
```
